Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
complete bib
update the Algorithm

\begin{enumerate}
\item Stochastic gradient descent (SGD) as a class of efficient Markov chain sampler
\item Proved stationary distribution
\item Fast sampler for any Bayesian posteriors
\item Derived upper bound on the mixing time based on convergence results
\end{enumerate}

@@

%------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{SGD Sampling Algorithm}

\begin{algorithm}[H]
{\small
Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
\begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
\STATE {\bf Initialize} $ \bx^0$ arbitrarily;
\WHILE{stopping criterion not satisfied}
\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
\STATE
$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
\STATE $k\gets k+1$;
\ENDWHILE
\STATE return $\bx^k$.
\end{algorithmic}}
\end{algorithm}

@@

\begin{itemize}
\item Email: \href{mailto:wang.yu@berkeley.edu}{wang.yu@berkeley.edu}
\item Email: \href{mailto:wcai@berkeley.edu}{wcai@berkeley.edu}
\end{itemize}

>>>>

\begin{enumerate}
\item Stochastic gradient descent (SGD) as a class of efficient Markov chain sampler
\item Derived the stationary distribution
\item Fast sampler for any Bayesian posteriors
\item Derived upper bound on the mixing time based on convergence results
\end{enumerate}

@@

%------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------
Suppose we would like to sample from a distribution $p(x) \propto f(x)$. 
\begin{block}{SGD Sampling Algorithm}

\begin{algorithm}[H]
{\small
Given $f(x)$, 
\begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
\STATE {\bf Initialize} $ \bx^0$ arbitrarily;
\WHILE{burn-in period}
\STATE draw $a^t$ from Gaussian distribution $\N(\nabla f(\bx^k), \Sigma^{t})$.
\STATE
$\bx^{k+1} \gets \bx^k - (\Sigma^t)^{-1} a^t$;
\STATE $k\gets k+1$;
\ENDWHILE
\STATE return $\bx^k$.
\end{algorithmic}}
\end{algorithm}

@@

\begin{itemize}
\item Email: \href{mailto:wang.yu@berkeley.edu, wcai@berkeley.edu}{\{wang.yu, wcai\}@berkeley.edu}
\end{itemize}
